---
name: Xiaofei
surname: Zhang
position: "Senior Scientist"
address: "4505 Redwood Circle, 55345, Minnetonka, MN"
phone: +1 612 802 8711
# www:
email: "xiaofei.zhang@cgiar.org"
# twitter: mariecurie
# github: mariecurie
linkedin: xiaofeibreeder
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Profile

 * Lead the global breeding team with purpose, trust, consistency, and credibility.
 * Have more than 10 years of experience in applied breeding pipeline management.
 * Manage multiple projects with approximately $3 Million every year.
 * Hands-on experience in processing large and complex breeding data.
 * Advanced ability to program in R to analyze data. 
 * Master statistics and experimental design.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "BS in Agronomy", "2000-04", "Shenyang Agricultural University", "Liaoning, China",
  "Ph.D. in Plant Breeding", "2004-10", "University of Chinese Academy of Sciences", "Beijing, China",
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Experience

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Postdoctoral Researcher", "2010-12", "Institute of Crop Sciences, Chinese Academy of Agricultural Sciences", "Beijing, China",
  "Research Associate-Breeder", "2012-17", "University of Minnesota", "Minnesota, USA",
  "Sweetpotato Breeder", "2017-19","North Carolina State University", "North Carolina, USA",
   "Global Cassava Breeding Lead", "2019-Now","The Alliance of Bioversity International and CIAT, CGIAR", "Cali, Colombia"
  
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Publications

1.	Hernán Ceballos, Clair Hershey, Carlos Iglesias, __Xiaofei Zhang__ (2021) Fifty years of a public cassava breeding program: evolution of breeding objectives, methods, and decision‑making processes. _Theoretical and Applied Genetics_ (2021) 134:2335–2353.
1.	Prabin Bajgain, __Xiaofei Zhang__, Jacob M. Jungers, Lee R. DeHaan, Brett Heim, Craig C. Sheaffer, Donald L. Wyse, James A. Anderson (2020) ‘MN-Clearwater’, the first food‐grade intermediate wheatgrass (Kernza perennial grain) cultivar. _Journal of Plant Registrations_.
1.	Prabin Bajgain, __Xiaofei Zhang__, James A. Anderson (2020) Dominance and G×E interaction effects improve genomic prediction and genetic gain in intermediate wheatgrass (Thinopyrum intermedium). _The Plant Genome_.
1.	Steve Larson, Lee DeHaan, Jesse Poland, __Xiaofei Zhang__, Kevin Dorn, Traci Kantarski, James Anderson, Jeremy Schmutz, Jane Grimwood, Jerry Jenkins, Shengqiang Shu, Jared Crain, Matthew Robbins & Kevin Jensen. (2019) Genome mapping of quantitative trait loci (QTL) controlling domestication traits of intermediate wheatgrass (Thinopyrum intermedium). _Theoretical and Applied Genetics_ v132, 2325–2351.
1.	Nidhi Rawat, Michael O. Pumphrey, Sixin Liu, __Xiaofei Zhang__, Vijay K. Tiwari, Harold N. Trick, William W. Bockus, Eduard Akhunov, James A. Anderson, and Bikram S. Gill. (2017) Wheat Fhb1 encodes a chimeric lectin with agglutinin domains and a pore-forming toxin-like domain conferring resistance to Fusarium head blight. _Nature Genetics_.
1.	__Xiaofei Zhang__, Ahmad Sallam, Liangliang Gao, Traci Kantarski, Jesse Poland, Donald L. Wyse, Lee DeHaan, James A. Anderson. (2016) Establishment and optimization of genomic selection to accelerate the domestication of intermediate wheatgrass (Thinopyrum intermedium). _The Plant Genome_.
1. And more on [__Google Scholar__](https://scholar.google.com/citations?hl=en&authuser=2&user=FgNoRpYAAAAJ)

```{r}
if (FALSE){
  # all public
  print ("1.	Samar Sheat, __Xiaofei Zhang__, Stephan Winter (2022) High-throughput virus screening in crosses of South American and African cassava germplasm reveals broad-sepectrum resistance against viruses causing cassava brown streak disease and cassava mosaic virus disease. _Agronomy_.
1.	Cu Thi Le Thuy, Luis Augusto Becerra Lopez-Lavalle, Nguyen Anh Vu, Nguyen Huu Hy, Pham Thi Nhan, Hernan Ceballos, Jonathan Newby, et al. __Xiaofei Zhang__ (2021) Identifying new resistance to cassava mosaic disease and validating markers for the CMD2 locus. _Agriculture_ 11, 829.
1.	Luis Augusto Becerra Lopez-Lavalle, Adriana Bohorquez-Chaux, __Xiaofei Zhang__ (2021) Identification of cassava varieties in ex-situ collections and global farmer’s fields: an update from 1990 to 2020. _Cassava - Biology, Production, and Use_.
1.	Hernán Ceballos, Clair Hershey, Carlos Iglesias, __Xiaofei Zhang__ (2021) Fifty years of a public cassava breeding program: evolution of breeding objectives, methods, and decision‑making processes. _ Theoretical and Applied Genetics_ (2021) 134:2335–2353.
1.	Thierry Tran, __Xiaofei Zhang__, Hernan Ceballos, Jhon L. Moreno, Jorge Luna, Andrés Escobar, Nelson Morante, John Belalcazar, Luis A. Becerra, Dominique Dufour (2020) Correlation of cooking time with water absorption and changes in relative density during boiling of cassava roots. International _Journal of Food Science & Technology_.
1.	Kayla R. Altendorf, Lee R. DeHaan, Garett C. Heineck, __Xiaofei Zhang__, James A. Anderson (2020) Floret site utilization and reproductive tiller number are primary components of grain yield in intermediate wheatgrass spaced plants. _Crop Science_.
1.	Prabin Bajgain, __Xiaofei Zhang__, Jacob M. Jungers, Lee R. DeHaan, Brett Heim, Craig C. Sheaffer, Donald L. Wyse, James A. Anderson (2020) ‘MN-Clearwater’, the first food‐grade intermediate wheatgrass (Kernza perennial grain) cultivar. _Journal of Plant Registrations_.
1.	Prabin Bajgain, __Xiaofei Zhang__, James A. Anderson (2020) Dominance and G×E interaction effects improve genomic prediction and genetic gain in intermediate wheatgrass (Thinopyrum intermedium). _The Plant Genome_.
1.	Jared Crain, Prabin Bajgain, James Anderson, __Xiaofei Zhang__, Lee DeHaan and Jesse Poland (2020) Enhancing Crop Domestication Through Genomic Selection, a Case Study of Intermediate Wheatgrass. _Frontier in Plant Science_.
1.	Steve Larson, Lee DeHaan, Jesse Poland, __Xiaofei Zhang__, Kevin Dorn, Traci Kantarski, James Anderson, Jeremy Schmutz, Jane Grimwood, Jerry Jenkins, Shengqiang Shu, Jared Crain, Matthew Robbins & Kevin Jensen. (2019) Genome mapping of quantitative trait loci (QTL) controlling domestication traits of intermediate wheatgrass (Thinopyrum intermedium). _Theoretical and Applied Genetics_ v132, 2325–2351.
1.	Prabin Bajgain, __Xiaofei Zhang__, M. Kathryn Turner, Rebecca D. Curlan, Brett Heim, Ruth Dill-Macky, Carol A. Ishimaru and James A. Anderson (2019) Characterization of Genetic Resistance to Fusarium Head Blight and Bacterial Leaf Streak in Intermediate Wheatgrass (Thinopyrum intermedium). _Agronomy_ 2019, 9(8), 429.
1.	Prabin Bajgain, __Xiaofei Zhang__, James A. Anderson. (2019) Genome-wide association study of yield component traits in Intermediate Wheatgrass and implications in genomic selection and breeding. _G3: Genes | Genomes | Genetics_ 2019, 9 (8), 2429-2439.
1.	__Xiaofei Zhang__, Liangliang Gao, Ahmad Sallam, Soon Li Teh, Donald L. Wyse, Lee DeHaan, James A. Anderson. (2017) Uncovering the Genetic Architecture of Seed Weight and Size in Intermediate Wheatgrass through Linkage and Association Mapping. _The Plant Genome_. 
1.	Nidhi Rawat, Michael O. Pumphrey, Sixin Liu, __Xiaofei Zhang__, Vijay K. Tiwari, Harold N. Trick, William W. Bockus, Eduard Akhunov, James A. Anderson, and Bikram S. Gill. (2017) Wheat Fhb1 encodes a chimeric lectin with agglutinin domains and a pore-forming toxin-like domain conferring resistance to Fusarium head blight. _Nature Genetics_.
1.	Traci Kantarski, Steve Larson, __Xiaofei Zhang__ (co-first author), Lee DeHaan, Justin Borevitz, James A. Anderson, Jesse Poland (2017). Development of the first consensus genetic map of intermediate wheatgrass (Thinopyrum intermedium) using genotyping-by-sequencing. _Theoretical and Applied Genetics_.
1.	__Xiaofei Zhang__, Ahmad Sallam, Liangliang Gao, Traci Kantarski, Jesse Poland, Donald L. Wyse, Lee DeHaan, James A. Anderson. (2016) Establishment and optimization of genomic selection to accelerate the domestication of intermediate wheatgrass (Thinopyrum intermedium). _The Plant Genome_.
1.	Michael Kantar, Catrin Tyl, Kevin Dorn, __Xiaofei Zhang__ (co-first author), Jacob Jungers, Joe Kaser, Rachel Schendel, James Eckberg, Bryan Runck, Mirko Bunzel, Nick Jordan, Robert Stupar, David Marks, James Anderson, Gregg Johnson, Craig Sheaffer, Tonya Schoenfuss, Baraem Ismail, George Heimpel, Donald Wyse. (2016) Perennial Grain and Oilseed Crops. _Annual Review of Plant Biology_.
1.	__Xiaofei Zhang__, Matthew N. Rouse, Itamar C. Nava, Yue Jin, James A. Anderson. Development and verification of wheat germplasm containing both Sr2 and Fhb1. _Molecular Breeding_ 36: 85.
1.	Lee DeHaan, David Van Tassel, James Anderson, Sean Asselin, Richard Barnes, Gregory Baute, Douglas Cattani, Steve Culman, Kevin Dorn, Brent Hulke, Michael Kantar, Steve Larson, M. David Marks, Allison Miller, Jesse Poland, Damian Ravetta, Emily Rude, Matthew Ryan, Don Wyse, and __Xiaofei Zhang__, (2016) A pipeline strategy for crop domestication. _Crop Science_ 56:917–930. 
1.	Liangliang Gao, Josh Kielsmeirer-Cook, Prabin Bajgain, __Xiaofei Zhang__, Matthew N. Rouse, Shiaoman Chao, Yue Jin and James A. Anderson (2015) Development of genotyping by sequencing (GBS) and array derived SNP markers for stem rust resistance gene Sr42. _Molecular Breeding_.
1.	__Xiaofei Zhang__, Jae-Bom Ohm, Steven Haring, Lee R. DeHaan, James A. Anderson (2015) Towards the understanding of end-use quality in intermediate wheatgrass (Thinopyrum intermedium): high-molecular-weight glutenin subunits, protein polymerization, and mixing characteristics. _Journal of Cereal Science_ 66: 81–88.
1.	Guangbin Luo, __Xiaofei Zhang__, Yanlin Zhang, Wenlong Yang, Yiwen Li, Jiazhu Sun, Kehui Zhan, Aimin Zhang, Dongcheng Liu. (2015) Composition, variation, expression and evolution of low-molecular-weight glutenin subunit genes in Triticum urartu. _BMC Plant Biology_. 15:68.
1.	Lee R. DeHaan, Shuwen Wang, Steven R. Larson, Douglas J. Cattani, __Xiaofei Zhang__, Traci Viinanen (2014) Current efforts to develop perennial wheat and domesticate Thinopyrum intermedium as a perennial grain. In: Batello C., Wade L., Cox S., Pogan N., Bozzini A., and Choptiany J. (ed) _Perennial crops for food security_: proceedings of the FAO expert workshop. FAO, Rome, Italy, pp72-89.
1.	__Xiaofei Zhang__, Lee R. DeHaan, LeeAnn Higgins, Todd W. Markowski, Donald L. Wyse, James A. Anderson (2014) New insights into high-molecular-weight glutenin subunits and subgenomes of the perennial crop Thinopyrum intermedium (Triticeae). _Journal of Cereal Science_. 59: 203-210.
1.	__Xiaofei Zhang__, Dongcheng Liu, Jianghua Zhang, Wei Jiang, Guangbin Luo, Wenlong Yang, Jiazhu Sun, Yiping Tong, Dangqun Cui, Aimin Zhang (2013) Novel insights into the composition, variation, organization, and expression of the low-molecular-weight glutenin subunit gene family in common wheat. _Journal of Experimental Botany_. 64: 2027-2040.
1.	HongQing Ling, Shancen Zhao, Dongcheng Liu, Junyi Wang, Hua Sun, Chi Zhang, Huajie Fan, Dong Li, Lingli Dong, Yong Tao, Chuan Gao, Huilan Wu, Yiwen Li, Yan Cui, Xiaosen Guo, Shusong Zheng, Biao Wang, Kang Yu, Qinsi Liang, Wenlong Yang, Xueyuan Lou, Jie Chen, Mingji Feng, Jianbo Jian, __Xiaofei Zhang__, et al. (2013) Draft genome of the wheat A-genome progenitor Triticum urartu. _Nature_. 496: 87-90.
1.	__Xiaofei Zhang__, Hui Jin, Yan Zhang, Dongcheng Liu, Genying Li, Xianchun Xia, Zhonghu He and Aimin Zhang (2012) Composition and functional analysis of low-molecular-weight glutenin alleles with Aroona near-isogenic lines of bread wheat. _BMC Plant Biology_. 12: 243.
1.	__Xiaofei Zhang__, Dongcheng Liu, Wei Jiang, Xiaoli Guo, Wenlong Yang, Jiazhu Sun, Hongqing Ling, Aimin Zhang (2011) PCR-based isolation and identification of full-length low-molecular-weight glutenin subunit genes in bread wheat (Triticum aestivum L.). _Theoretical and Applied Genetics_.123: 1293-1305.
1.	__Xiaofei Zhang__, Dongcheng Liu, Wenlong Yang, Kunfan Liu, Jiazhu Sun, Xiaoli Guo, Yiwen Li, Daowen Wang, Hongqing Ling, Aimin Zhang (2011) Development of a new marker system for identifying the complex members of the low-molecular-weight glutenin subunit gene family in bread wheat (Triticum aestivum L.). _Theoretical and Applied Genetics_. 112: 1503-1516
1.	Lingli Dong, __Xiaofei Zhang__ (co-first author), Dongcheng Liu, Huajie Fan, Jiazhu Sun, Zhongjuan Zhang, Huanju Qin, Bin Li, Shanting Hao, Zhensheng Li, Daowen Wang, Aimin Zhang, Hongqing Ling (2010) New insights into the organization, recombination, expression and functional mechanism of low molecular weight glutenin subunit genes in bread wheat. _PLoS ONE_. 5(10): e13548.")
}
```

